---
title: "Investigating Wafer Data"
author: "Peter Czerner"
format: html
editor: visual
---

## Install needed packages

We used the package [`renv`](https://cran.r-project.org/web/packages/renv/index.html), to record packages used and make you able to recover the package environment, after you checked out this project from github. All what you need is to run the following command:

```{r}
renv::restore()
```

Now the needed packages with dependencies are installed, and we can load, what we need:

```{r}
library(data.table)
library(ggplot2)
```

## Wafer map template data

I have prepared a wafer map template in this project. You canfind them in directory data. It has three components, that we will load here

```{r}
# Initialize a list
wtemplate<-list()
```

### Master data

```{r}
print(wtemplate$master<-readRDS("data/map_template.Rds"))
```

### Stepper field data

```{r}
print(head(wtemplate$sf<-readRDS("data/sf_table.Rds"),5))
```

### Die data

```{r}
print(wtemplate$dice<-readRDS("data/die_table.Rds"))
```

## Plot map template

As the first step we plot a circle representing an empty wafer. Befor we can do that, we need to define a little help function to extend the package [`ggplot2`](https://cran.r-project.org/web/packages/ggplot2/index.html):

```{r}
circleFun <- function(center = c(0,0),diameter = 1, npoints = 100){
    r = diameter / 2
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    df<-data.frame(x = xx, y = yy)
    
    geom_path(data=df, aes(x,y))
    
}
```

Now we can start to plot:

### Empty wafer

Here we use our circle function and wafer diameter as loaded from data:

```{r fig.asp=1}
ggplot() + circleFun(diameter=wtemplate$master$wafer_size)
```

### Stepper fields

To plot stepper fields we use [`geom_rect`](https://ggplot2.tidyverse.org/reference/geom_tile.html) from package [`ggplot2`](https://ggplot2.tidyverse.org/index.html) and our prepared stepper field data. We also use [`geom_text`](https://ggplot2.tidyverse.org/reference/geom_text.html) to write out the stepper field numbers:

```{r fig.asp=1}
ggplot(wtemplate$sf) +
  geom_rect( 
            aes(
              xmin=sf_xmin, 
              xmax=(sf_xmin+wtemplate$master$step_x), 
              ymin=sf_ymin, 
              ymax=(sf_ymin+wtemplate$master$step_y)), 
            fill=NA, colour="blue")+
  circleFun(diameter=wtemplate$master$wafer_size) +
  geom_text(aes(
    x=sf_xmin+wtemplate$master$step_x/2, 
    y=sf_ymin+wtemplate$master$step_y/2, 
    label=sf_id), 
   size=5, 
   colour="darkgrey"
  )
```

### Dice

Same procedure for dice. here we use the attribute `die_type` to fill the dice to distinguish between potential good dice and edge dice.

As we can see, all the map components can be simply added together:

```{r fig.asp=.8}
ggplot() +
  # Dice
  geom_rect(data=wtemplate$dice,
            aes(
              xmin=die_xmin, 
              xmax=(die_xmin+wtemplate$master$die_x), 
              ymin=die_ymin, 
              ymax=(die_ymin+wtemplate$master$die_y),
              fill=die_type
              ), 
            colour="black") +
  # Stepper fields
  geom_rect(data=wtemplate$sf,
            aes(
              xmin=sf_xmin, 
              xmax=(sf_xmin+wtemplate$master$step_x), 
              ymin=sf_ymin, 
              ymax=(sf_ymin+wtemplate$master$step_y)), 
            fill=NA, colour="blue") +
  # Wafer circle
  circleFun(diameter=wtemplate$master$wafer_size)
```

## Investigate test data

Prepared test data are stored in the file `test_data.Rds`. Let us load it:

```{r}
test_values<-readRDS("data/test_data.Rds")
test_values[1:5]
```

Because of storage efficiency, the table includes only die_id and the test value. The die coordinates are stored separately:

```{r}
die_data<-readRDS("data/die_id_table.Rds")
die_data[1:5]
```

Now we join both tables, to be able to investigate the data in the context of the coordinates:

```{r}
test_data<-die_data[test_values, on="die_id"]
test_data[1:5]
```

Last but not leas we load the test limits:

```{r}
lim<-readRDS("data/test_limits.Rds")
lim
```

### Compute simple statistics

First step in each data investigation is to compute simple statistics. [`data.table`](https://cran.r-project.org/web/packages/data.table/vignettes/datatable-intro.html) package is very useful for this purpose:

```{r}
test_data[,.(
  die_count = .N,
  nok       = sum(ifelse(between(test_value,lim$low,lim$high),0,1)),
  mean      = mean(test_value),
  sd        = sd(test_value),
  cp        = (lim$high-lim$low)/6*sd(test_value),
  cpk       = min(lim$high-mean(test_value),mean(test_value)-lim$low)/3*sd(test_value)
), by=wafer_nr]



```

### Plot value histogram

We plot a histogram of test values and distinguish the wafer numbers using different colors:

```{r}
ggplot(test_data) +
  geom_histogram(aes(
     x=test_value, 
     group=factor(wafer_nr), 
     fill=factor(wafer_nr)),
    alpha = .5, bins = 100) +
  geom_vline(xintercept = c(-2,2), color="red", linetype="dashed") +
  labs(
    title="Test value histogram",
    x="Test value",
    y="Count",
    fill="Wafer No."
  )
```

### Plot wafer map

#### One wafer

We plot the wafer map for test values of wafer 1. We use test limits to set the color scale between the limits, all values outside of limits are grey:

```{r fig.asp=.8}
ggplot() +
  # Dice
  geom_rect(data=test_data[wafer_nr==1],
            aes(
              xmin=die_xmin, 
              xmax=(die_xmin+wtemplate$master$die_x), 
              ymin=die_ymin, 
              ymax=(die_ymin+wtemplate$master$die_y),
              fill=test_value
              )) +
  # Wafer circle
  circleFun(diameter=wtemplate$master$wafer_size) +
  scale_fill_gradient(limits=unlist(lim))
```

#### Stack map

For some purposes it is useful to plot a stack wafer map over all wafers of a lot:

```{r}
mean_values<-test_data[,.(mean_value=mean(test_value)), by=.(die_xmin,die_ymin)]
```

```{r fig.asp=.8}
ggplot() +
  # Dice
  geom_rect(data=mean_values,
            aes(
              xmin=die_xmin, 
              xmax=(die_xmin+wtemplate$master$die_x), 
              ymin=die_ymin, 
              ymax=(die_ymin+wtemplate$master$die_y),
              fill=mean_value
              )) +
  # Wafer circle
  circleFun(diameter=wtemplate$master$wafer_size) +
  scale_fill_gradient(limits=c(-2,2))
```

Indeed, some structures can be recognized here.

#### All wafers iin one plot

We can easy plot all wafers at once using [facet_wrap](https://ggplot2.tidyverse.org/reference/facet_wrap.html) method:

```{r fig.asp=.5}
ggplot() +
  # Dice
  geom_rect(data=test_data,
            aes(
              xmin=die_xmin, 
              xmax=(die_xmin+wtemplate$master$die_x), 
              ymin=die_ymin, 
              ymax=(die_ymin+wtemplate$master$die_y),
              fill=test_value
              ), show.legend = FALSE) +
  # Wafer circle
  circleFun(diameter=wtemplate$master$wafer_size) +
  scale_fill_gradient(limits=unlist(lim)) +
  # Split over wafers
  facet_wrap(wafer_nr~.,ncol = 4) + 
  # Remove all labels
  theme_void()
 
```

Here you can better recognize the problems we are facing with individual wafers.

In the real world it is very useful to wrap all the commands into methods like `plotWafermap(lot=12345, wafer=1:5, method="stack")`... ðŸ˜

\-\--

Created by Peter Czerner, January 2024
